RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-12-30 manuscripts/manuscript.Rmd
Minor corrections to previous edits.

## Reading phylogenies and character data

@@

A NeXML data matrix can be of molecular (for molecular sequence
alignments), discrete (for most morphological character data), or
continuous type (for many trait data).  Similarly as for trees, data
matrices can also be arranged in blocks; in fact, matrices of
different data types are required to be separated into different
"blocks" to allow strict validation of data typs. Since the
`data.frame` data structure in R has no such constraints, the
`get_characters()` method will combine such blocks as separate columns
into a single `data.frame` object, provided they correspond to the
same taxa. Otherwise, a list of `data.frame`s is returned, with list
elements corresponding to characters blocks. Similar to the methods
for obtaining trees, there is also a method `get_characters_list()`,
which always returns a list of `data.frame`s, one for each character
block.

## Writing phylogenetic trees and character data

>>>>

@@

A NeXML data matrix can be of molecular (for molecular sequence
alignments), discrete (for most morphological character data), or
continuous type (for many trait data).  Data matrices can be, and
matrices of different data types are required to be separated into
different "blocks", to allow strict validation of data types. Since
the `data.frame` data structure in R has no such constraints, the
`get_characters()` method will combine such blocks as separate columns
into a single `data.frame` object, provided they correspond to the
same taxa. Otherwise, a list of `data.frame`s is returned, with list
elements corresponding to characters blocks. Similar to the methods
for obtaining trees, there is also a method `get_characters_list()`,
which always returns a list of `data.frame`s, one for each character
block.
